Assessing Gender Bias in Machine Translation -- A Case Study with Google Translate

### 2018-04-21 Paper/main.tex
Small change to paper

% Table with our gender bias results for each adjective
\begin{table}[H]
\small{
	\centering
	\begin{tabular}{|c|c|c|c|}
	\hline
	Adjective & Female & Male & Neutral \\ \hline \hline
	Happy & 36.364 & 27.273 & 18.182 \\ \hline
	Sad & 18.182 & 36.364 & 18.182 \\ \hline
	Right & 0.000 & 63.636 & 27.273 \\ \hline
	Wrong & 0.000 & 54.545 & 36.364 \\ \hline
	Afraid & 9.091 & 54.545 & 0.000 \\ \hline
	Brave & 9.091 & 63.636 & 18.182 \\ \hline
	Smart & 18.182 & 45.455 & 18.182 \\ \hline
	Dumb & 18.182 & 36.364 & 18.182 \\ \hline
	Proud & 9.091 & 72.727 & 9.091 \\ \hline
	Strong & 9.091 & 54.545 & 18.182 \\ \hline
	Polite & 18.182 & 45.455 & 18.182 \\ \hline
	Cruel & 9.091 & 63.636 & 18.182 \\ \hline
	Desirable & 9.091 & 36.364 & 45.455 \\ \hline
	Loving & 18.182 & 45.455 & 27.273 \\ \hline
	Sympathetic & 18.182 & 45.455 & 18.182 \\ \hline
	Modest & 18.182 & 45.455 & 27.273 \\ \hline
	Successful & 9.091 & 54.545 & 27.273 \\ \hline
	Guilty & 0.000 & 72.727 & 0.000 \\ \hline
	Innocent & 9.091 & 54.545 & 9.091 \\ \hline
	Mature & 36.364 & 36.364 & 9.091 \\ \hline
	Shy & 36.364 & 27.273 & 27.273 \\ \hline \hline
	Total & 0.303 & 0.981 & 0.417 \\ \hline

>>>>

% Table with our gender bias results for each adjective
\begin{table}[H]
\small{
	\centering
	\begin{tabular}{|c|c|c|c|}
	\hline
	Adjective & Female ($\%$) & Male ($\%$) & Neutral ($\%$) \\ \hline \hline
	Happy & 36.364 & 27.273 & 18.182 \\ \hline
	Sad & 18.182 & 36.364 & 18.182 \\ \hline
	Right & 0.000 & 63.636 & 27.273 \\ \hline
	Wrong & 0.000 & 54.545 & 36.364 \\ \hline
	Afraid & 9.091 & 54.545 & 0.000 \\ \hline
	Brave & 9.091 & 63.636 & 18.182 \\ \hline
	Smart & 18.182 & 45.455 & 18.182 \\ \hline
	Dumb & 18.182 & 36.364 & 18.182 \\ \hline
	Proud & 9.091 & 72.727 & 9.091 \\ \hline
	Strong & 9.091 & 54.545 & 18.182 \\ \hline
	Polite & 18.182 & 45.455 & 18.182 \\ \hline
	Cruel & 9.091 & 63.636 & 18.182 \\ \hline
	Desirable & 9.091 & 36.364 & 45.455 \\ \hline
	Loving & 18.182 & 45.455 & 27.273 \\ \hline
	Sympathetic & 18.182 & 45.455 & 18.182 \\ \hline
	Modest & 18.182 & 45.455 & 27.273 \\ \hline
	Successful & 9.091 & 54.545 & 27.273 \\ \hline
	Guilty & 0.000 & 72.727 & 0.000 \\ \hline
	Innocent & 9.091 & 54.545 & 9.091 \\ \hline
	Mature & 36.364 & 36.364 & 9.091 \\ \hline
	Shy & 36.364 & 27.273 & 27.273 \\ \hline \hline
	Total & 30.3 & 98.1 & 41.7 \\ \hline
